---
output:
  html_document:
    code_folding: null
    keep_md: false
    mathjax: null
    self_contained: false
    number_sections: no
    highlight: null
    toc: no
    includes:
      before_body: resources/header.html
      after_body:  resources/footer.html
    theme: yeti
    md_extensions: -autolink_bare_uris
---

```{r buildXML_loadpkgs, echo=FALSE, results = "hide", message = FALSE, warnings=FALSE, tidy=TRUE, include = FALSE}

# Note, this code runs in `builder` as the working directory.

library(leaflet, quietly = TRUE, verbose = FALSE)
library(RPostgreSQL, quietly = TRUE, verbose = FALSE)
library(httr, quietly = TRUE, verbose = FALSE)

table <- readr::read_csv('neotomadois.csv')

if (ds_id %in% table$neotoma_dataset) {
  dois <- table %>% 
    filter(ds_id %in% table$neotoma_dataset) %>% 
    select(doi)
}

# Note, this is being run by a knit command in another document, so 
# ds_id is being passed in from the external script:

source('R/call_sql.R')

sql_calls <- readr::read_csv('doi_sens.csv') %>% call_sql(ds_id = ds_id)

```

<title>`r sql_calls$defaults$sitename[1]` - Neotoma Dataset `r ds_id`</title>

# Neotoma Dataset `r ds_id`

## `r sql_calls$defaults$sitename[1]`

<div style="float: right;">
```{r leaflet_map, echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE, fig.width=3, fig.height=3}

new_map <- leaflet() %>% 
  addProviderTiles('Esri.WorldImagery') %>% 
  addProviderTiles('Stamen.TonerBackground',
                   options = providerTileOptions(opacity = 0.45)) %>% 
  addProviderTiles("Stamen.TonerLabels")

# Now we have to pull out the lat/longs:
locs <- sql_calls$locs %>% as.numeric()

popup_content <- paste0("<b>",default$sitename[1],"</b>",
                        "<br>View in <a href=http://apps.neotomadb.org//explorer/?datasetid=", 
                        ds_id, ">Explorer</a>")

if (locs[1] == locs[3] & locs[2] == locs[4]) {
  new_map <- addMarkers(new_map, 
                        popup = popup_content, 
                        lng = locs[2], lat = locs[3]) %>% 
    setView(lng = locs[2], lat = locs[1], zoom = 5)
} else {
  new_map <- addPolygons(new_map, 
                         lng = c(locs[c(2,4, 4, 2)]), 
                         lat = c(locs[c(1,1, 3, 3)]), popup = popup_content) %>%
    addMarkers(new_map, 
               popup = popup_content, 
               lng = locs[2], 
               lat = locs[3]) %>% 
    setView(lng = locs[2], lat = locs[1], 
            zoom = 7)
}

new_map

```
</div>

```{r, echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE}
# TODO add the thing if it's in the table or not.

if(ds_id %in% table$neotoma_dataset) {
  good_doi <- TRUE
  doi <-  table %>% filter(neotoma_dataset == ds_id) %>% select(doi) %>% unlist()
} else {
  good_doi <- FALSE
}
```

```{r conditional_block, echo=FALSE, results='asis', eval=good_doi}

for (i in 1:length(doi)) {
  cat('**DOI**: [', doi[1], '](`r paste0("http://dx.doi.org/", doi[1])`)\n')
}

```

**Links**: [View on Neotoma Explorer](http://apps.neotomadb.org/explorer/?datasetid=`r ds_id`) | [Download JSON](http://api.neotomadb.org/v1/data/downloads/`r ds_id`) | [Download zipped CSV](http://api.neotomadb.org/v1/data/downloads/`r ds_id`?format=csv)

**Constituent Database**: `r sql_calls$constituent %>% as.character()`

**Dataset Type**: `r sql_calls$sites$datasettype[which(sql_calls$sites$datasetid == ds_id)]`

**Latitude**: `r ifelse(locs[1] == locs[3], locs[1], paste0('[',locs[1], ',', locs[3], ']'))`

**Longitude**: `r ifelse(locs[2] == locs[4], locs[2], paste0('[',locs[2], ',', locs[4], ']'))`

```{r, echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE}

agerange <- sql_calls$range

if (nrow(agerange) == 0) {
  range_out <- "No relevant chronology."
} else {
  range_out <- paste0(agerange[1], ' -- ', agerange[2], ' ', as.character(agerange$AgeType))
}

```

**Age Range**: `r range_out`

**Description**: `r ifelse(is.na(sql_calls$descrip), "No description provided", sql_calls$descrip) %>% as.character()`

<br>

## Affiliated Researchers

```{r getContacts, results='as-is', echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE}

contacts <- sql_calls$contacts
contacts <- apply(contacts, 2, function(x){ iconv(x, "UTF-8", 'latin1')})

contacts[,"affiliation"] <- gsub('\r\n', ', ', contacts[,"affiliation"])
colnames(contacts) <- c("Name", "Affiliation", "Contribution")

contacts <- contacts[order(contacts[,1]), ]
contacts <- contacts[!duplicated(contacts),]

knitr::kable(contacts, row.names = FALSE)

```


## Publications

```{r, echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE, results='as-is'}
publications <- sql_calls$publn
#publications[,4] <- iconv(publications[,4], "UTF-8", "latin1")

if (nrow(publications) > 0) {
  knitr::kable(publications[,c(1,4)])
} else {
  print("No publications in this record.")
}

```

## Data Citation

```{r, echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE}

authors <- paste0(contacts[which(contacts[,"Contribution"] == "ProjectLeader"),1], collapse = ', ')

if(unlist(sql_calls$constituent) == "FAUNMAP") {
  authors <- paste0(contacts[which(contacts[,"Contribution"] == "Researcher"),1], 
                    collapse = ', ')
  
}

plain_text <- paste0(authors, ". ",
       max(lubridate::year(sql_calls$dates$dataset)),
       ". ",
       sql_calls$defaults$sitename[1], ". In, *",
       sql_calls$constituent[1], "*. ",
       "Neotoma Paleoecological Database.")

if (good_doi) {
  plain_text <- paste0(plain_text, " doi: ", doi[1])
} else {
  plain_text <- paste0(plain_text, " URL: http://apps.neotomadb.org/explorer/?datasetid=", ds_id)
}
       
bibtex <- paste0("@inbook{<br>&nbsp;&nbsp;author={",
                 authors,
                 "},<br>&nbsp;&nbsp;year={",
                 max(lubridate::year(sql_calls$dates$dataset)),
                 "},<br>&nbsp;&nbsp;title={",
                 sql_calls$defaults$sitename[1], "},<br>&nbsp;&nbsp;booktitle={",
                 sql_calls$constituent[1], 
                 "},<br>&nbsp;&nbsp;publisher={",
                 "Neotoma Paleoecological Database},", collapse = ', ')

if (good_doi) {
  bibtex <- paste0(bibtex, 
                   "<br>&nbsp;&nbsp;doi={",
                   doi[1],"}<br>}<br>")
} else {
  bibtex <- paste0(bibtex, 
                   "<br>&nbsp;&nbsp;url={http://apps.neotomadb.org/explorer/?datasetid=", 
                   ds_id,"}<br>}<br>")
}

```

### APA

`r plain_text`

### BibTeX

`r bibtex`

## Other Associated Datasets

### Other Datasets at Same Site:

```{r, results = 'asis', echo=FALSE, message = FALSE, warnings=FALSE, tidy=TRUE}

sharedds <- sql_calls$sites

sharedds <- sharedds %>% filter(!datasetid == ds_id) %>% 
  select(dataset, datasetid)

if (nrow(sharedds) > 0) {
  sharedds$JSON <- paste0("[link](http://api.neotomadb.org/v1/data/downloads/",sharedds[,2],")")
  sharedds$Explorer <- paste0("[link](http://apps.neotomadb.org/explorer/?datasetid=",sharedds[,2],")")
  knitr::kable(sharedds[,-2], row.names = FALSE)
} else {
  cat("No other datasets at this site.")
}
```

### Most recent Neotoma Database snapshot: 

[http://www.neotomadb.org/snapshots](http://www.neotomadb.org/snapshots)

## Neotoma Data Use Policy 

We ask all data users to consider the Neotoma Data Use policy -- [link](http://www.neotomadb.org/data/category/use) -- as well as the general guidelines of open and ethical data sharing when using this data.

<script type="application/ld+json">
{
  "@context": "http://schema.org",
  "@type": "Dataset",
  "license": "https://creativecommons.org/licenses/by/4.0/deed.en_US",
  "author": {
    "@type":"Person",
    "name":"`r contacts[which(contacts[,"Contribution"] == "ProjectLeader"),1]`"
  },
  "includedInDataCatalog": {
    "@type": "DataCatalog",
    "about": "Paleoecology",
    "publisher": {
      "@type": "Organization",
      "name": "Neotoma Paleoecological Database",
      "alternateName":"Neotoma",
      "description":"The Neotoma Paleoecology Database and Community is an online hub for data, research, education, and discussion about paleoenvironments.",
      "url": "http://neotomadb.org"
    },
    "funder": {
      "@type":"Organization",
      "name":"National Sciences Foundation",
      "alternateName": "NSF",
      "url": "http://nsf.gov"
    }
  },
  "about": "`r sharedds$DatasetType[which(sharedds$DatasetID == ds_id)]`",
  "distribution":{
    "@type":"DataDownload",
    "contentUrl":"`r paste0("http://api.neotomadb.org/v1/data/downloads/",sharedds[,2])`",
    "datePublished": "`r Sys.time()`",
    "inLanguage": "en"
  },
  "spatialCoverage": {
    "@type": "Place",
    "name": "`r default$SiteName[1]`",
    "geo": {
        "@type": "GeoCoordinates",
        "latitude": "`r mean(locs[1], locs[3])`",
        "longitude": "`r mean(locs[2], locs[4])`",
        "elevation": "`r `"
    }
  }
}
</script>